Free surface computations in mantle convection models

### 2015-11-06 free-surface-paper.tex
add section overview

Here we analyze the problem of the sloshing instability.  We demonstrate the nature of the instability, 
as well as clarifying the effect of quasi-implicit stabilization.
The analysis allows us to propose a new time marching scheme for free surface computations with 
good stability properties. It is an explicit method which requires no modification to the system matrix,
which makes it extremely simple to implement.

Finally, we describe the implementation of a free surface in the mantle convection software \texttt{ASPECT}.

@@

\section{Quasi-implicit stabilization}
\label{sec:kmm}

@@

\section{A novel time-integration scheme}

@@

\section{Results}

>>>>

The paper is organized as follows.
After introducing the problem in Section~\ref{sec:governing},
we derive an approach to analyze 
free surface schemes based on the normal modes in Section~\ref{sec:eigenvalue}
and Section~\ref{sec:timestepping}.
In Section~\ref{sec:kmm} we use this approach to look at the
quasi-implicit stabilization proposed in \citet{kaus2010stabilization}.
Then, we propose a new time marching scheme for free surface computations with 
good stability properties (Section~\ref{sec:newscheme}).
Finally, we describe the implementation of a free surface in the mantle convection software \texttt{ASPECT} in Section~\ref{sec:implementation}, before showing numerical results
in \ref{sec:results}.

@@

\section{Analysis of quasi-implicit stabilization}
\label{sec:kmm}

@@

\section{A novel time-integration scheme}
\ref{sec:newscheme}

@@

\section{Results}
\label{sec:results}
